Historical aerial surveys map long-term changes of forest cover and structure in the central Congo Basin

### 2020-02-09 manuscript/main.Rmd
caption

```{r echo = FALSE, eval = TRUE}
change_stats %>%
  kable(caption="Land use land cover change statistics of forest cover around Yangambi in the central Congo Basin. The data evaluates a difference between a historical (1958) aerial photography based survey and the Hansen et al. 2013 based satellite remote sensing data. Spatial coverage statistics are provided hectares (ha), rounded to the nearest integer as well as Above Ground Carbon (AGC) scaled using recent survey measurements.",
       booktabs = TRUE,
       digits = 3,
       row.names = TRUE,
       escape = FALSE,
       col.names = c("ha",
                     "Gg C")
         ) %>%
    add_header_above(c(" " = 2,"AGC" = 1)) %>%
    #pack_rows("",1,1) %>%
    kable_styling(latex_options = c("hold_position"))
```

>>>>

```{r echo = FALSE, eval = TRUE}
change_stats %>%
  kable(caption="Land use land cover change statistics of forest cover around Yangambi in the central Congo Basin. The data evaluates a difference between a historical (1958) aerial photography based survey and the Hansen et al. 2013 based satellite remote sensing data. Spatial coverage statistics are provided hectares (ha), rounded to the nearest integer as well as Above Ground Carbon (AGC) scaled using recent survey measurements. Both non-forest cover in 1958 and the forest edge area are subsets of the original data (see Figure 6) and do not count toward the total scene area.",
       booktabs = TRUE,
       digits = 3,
       row.names = TRUE,
       escape = FALSE,
       col.names = c("ha",
                     "Gg C")
         ) %>%
    add_header_above(c(" " = 2,"AGC" = 1)) %>%
    #pack_rows("",1,1) %>%
    kable_styling(latex_options = c("hold_position"))
```

### 2020-02-09 manuscript/main.tex
caption

\caption{\label{tab:unnamed-chunk-10}Land use land cover change statistics of forest cover around Yangambi in the central Congo Basin. The data evaluates a difference between a historical (1958) aerial photography based survey and the Hansen et al. 2013 based satellite remote sensing data. Spatial coverage statistics are provided hectares (ha), rounded to the nearest integer as well as Above Ground Carbon (AGC) scaled using recent survey measurements.}
\centering
\begin{tabular}[t]{lrl}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{AGC} \\
\cmidrule(l{3pt}r{3pt}){3-3}
  & ha & Gg C\\
\midrule
Total scene area & 93431 & \\
Non-forest cover (1958) & 16200 & \\
Forest cover & 68455 & \\
-  of which forest edges & 13151 & \\
reforestation >1958 & 9918 & 811 - 1592\\
\addlinespace
deforestation >2000 & 8776 & 1408 $\pm$ 209\\
deforestation >1958 (permanent) & 6282 & 1008 $\pm$ 150\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:unnamed-chunk-10}Land use land cover change statistics of forest cover around Yangambi in the central Congo Basin. The data evaluates a difference between a historical (1958) aerial photography based survey and the Hansen et al. 2013 based satellite remote sensing data. Spatial coverage statistics are provided hectares (ha), rounded to the nearest integer as well as Above Ground Carbon (AGC) scaled using recent survey measurements. Both non-forest cover in 1958 and the forest edge area are subsets of the original data (see Figure 6) and do not count toward the total scene area.}
\centering
\begin{tabular}[t]{lrl}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{AGC} \\
\cmidrule(l{3pt}r{3pt}){3-3}
  & ha & Gg C\\
\midrule
Total scene area & 93431 & \\
Non-forest cover (1958) & 16200 & \\
Forest cover & 68455 & \\
-  of which forest edges & 13151 & \\
reforestation >1958 & 9918 & 811 - 1592\\
\addlinespace
deforestation >2000 & 8776 & 1408 $\pm$ 209\\
deforestation >1958 (permanent) & 6282 & 1008 $\pm$ 150\\
\bottomrule
\end{tabular}
\end{table}
